Databrary: Enabling sharing and reuse of research video

### 2015-04-14 jcdl-15/paper_demo.tex
some meager changes

Though Databrary also strongly encourages sharing and reuse as a complement to data storage and management.
As such, we have put a priority on creating an interface that allows other researchers to find, filter, and download video files they might be able to use in their own research or classroom teaching. 
Currently basic text search over the entire repository is supported and soon we will begin to implement more refined search that allows faceting of search results based on tags, keywords, and session metadata such as participant age group, task, study condition, and location.
Additionally, we allow for the creation of tags that annotate videos and video segments, which will also serve as an index point for this more refined search functionality.  
Each dataset comes with a formatted citation, a persistent URI, and soon will also mint and provide a DOI for referencing in scholarly publications and presentations.
Based on input from site users we have also built in the ability to excerpt or highlight clips from videos in such a way that they might serve as an exemplar clip for the dataset or be used in the classroom as an education tool or at professional conferences.
As we continue to hear feedback from our intended user base, we not only see Databrary as a tool that facilitates the management of research data, but also as an opportunity to enhance the ability for academics to communicate about their research in all of its richness.

>>>>

Though central to Databrary's mission is not merely the storage and management of research data, but making that data discoverable by other researchers and facilitating the reuse of that data in future studies and in scholarly communication as a citeable resource as well as an aid to educational presentation.
Currently basic text search over the entire repository is supported and soon we will begin to implement more refined search that allows faceting of search results based on tags, keywords, and session metadata such as participant age group, task, study condition, and location.
Additionally, Databrary allows for the annotatation of videos and video segments with tags, which will also serve as an index point for this more refined search functionality.

To aid in using datasets as a bibliographic source, each dataset comes with a formatted citation, a persistent URI, and soon will also be assigned a Digital Object Identifier (DOI) for referencing in scholarly publications and presentations.
Based on input from site users we have also built in the ability to excerpt or highlight clips from videos in such a way that they might serve as an exemplar clip for the dataset or be used in the classroom as an education tool or at professional conferences.
As we continue to gather feedback from our intended user base, we not only see Databrary as a tool that facilitates the standardized management of research data, but also as an opportunity to enhance the ability for academics communicate about their research in all of its richness.
